### 2021-07-22 doc/thesis/chapters/implementation.tex
axi lite register engine

%\includepicture [1.02] [0] [H] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/draw.io/bd_dsp_detailed}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{TODO: Other Stuff...}

>>>>

%see duplicate below
%\includepicture [1.02] [0] [H] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/draw.io/bd_dsp_detailed}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}

The main interfaces of the FM radio receiver IP are two AXI4-Stream interfaces and one AXI4-Lite memory-mapped slave interface.
The streaming interfaces are used for the input of IQ samples and output of the processed audio samples, while the memory-mapped interface provides configuration options and status information.

%%%%%
\subsubsection{AXI4-Stream}

An AXI4-Stream interface in the minimum configuration includes signals for the ready-indicator, and the data with its valid-indicator.
The ready-indicator is used as a flag to signalize whether the interface can process data or not at this time, which allows handshaking between subsequent processing blocks.
An IP may indicate that it is not ready, while its current operation is still running, for example.\\

In the VHDL version of the FM radio receiver IP, this handshaking is not implemented according to the AXI stream specification.
Specifically, the ready signal handshake is implemented with a workaround, to simplify the development.
The DSP chain of the IP is not fully pipelined and thus cannot consume an input sample on every clock cycle.
This is mainly because of the FIR filter implementation - it takes multiple clock cycles to compute an output sample, before it can take a new sample.
Ideally, this situation should be handled by the ready signal, since this is exactly what it is intended for.
However, in order to simplify the implementation a strobe generator is used, which is a counter that generates a repetitive pulse with a defined period.
This pulse, in combination with some additional logic, is used as the ready signal, to guarantee enough spacing between two consecutive input samples.

%%%%%
\subsubsection{AXI4-Lite Slave}

The IP provides configuration registers and status registers on this memory-mapped bus interface.
It is connected with the CPU, which uses these registers in the application software.\\

The VHDL code for this register interface is generated by a 'Register Engine' Python script.
The registers can be defined in a YAML-file.
Additionally, documentation in the form of a Markdown language file is generated, and - more importantly - a C/\cplusplus\ code header, which defines all the register addresses and can be used in the application software.\\

Fig.\ref{fig:register_engine} gives an overview of how the Register Engine script works.
The Python script takes the register definitions from the YAML file, and uses templates to generate the respecitive output files.\\

\includepicture [1.0] [0] [H] {Overview of the Register Engine script.} {register_engine} {img/draw.io/register_engine}

### 2021-07-22 doc/thesis/chapters/introduction.tex
comments
move the entire section vhdl:testbench:general to hls:testbench:general
axi lite register engine

In the view of a system design approach, another focus is put on a sustainable testing and development strategy for the entire system.
Above mentioned implementation variants should optimally share as much as possible of testing and verification code, in order to save time and effort in implementation.
Also, as many tasks as possible should be automated by scripts, to save time in manual labor for the engineers working on the development.
All that enables an efficient development cycle of the product.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NOTES:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%Thesis Design Decisions: \\
%\\
%Main focus on system design. \\
%\\
%How to achieve the same result in 3 (4?) different levels of abstraction?
%
%\begin{enumerate}
%  \item GnuRadio (?)
%  \item Matlab/Python
%  \item HLS\\
%      Implementation targeting Xilinx' ZedBoard.\\
%      Optionally: \\
%      Intel as a comparison (synth only, no HW) - "How platform-independent is HLS?"
%  \item VHDL
%\end{enumerate}
%\vspace{.5 cm}
%
%Compare:
%- Implementation effort (difficulty)
%- Implementation time
%- Usefulness on Target Systems (uC, SoC, RasPi, etc)
%- others?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FEEDBACK, Meeting 07-16-2021
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%formatting:
%- absätze überall gleich (mit oder ohne leerzeile)
%references:
%- hauptsache überall gleich (Fig.2.3 oder Sec.7.1 oder Eq.3 oder Chpt.4)
%- literature refs at the beginning of a chapter/section
%  like "this chapter is based on [1][4][5]."
%  or at the end of the last sentence like "...the end of this sentence. [7]"
%
%Allgemeiner Teil / Theorie:
% zusätzliches kapitel:
%   system design ansätze
%   - from algo to VHDL (book: vom algorithmus zur hardware)
%   - matlab to VHDL
%   - systementwuf richtung test driven design
%   --> design space exploration
%
%
% ganze Arbeit aufhängen an:
%   main objective: fit all the aspects (algorithm, impl, testing) into
%                   a single project
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO General
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% ## unify all graphs and diagrams
%       - all gray; use exact same gray tone; eliminate the yellow?
%
%

>>>>

In the view of a system design approach, another focus is put on a sustainable testing and development strategy for the entire system.
Above mentioned implementation variants should ideally share as much as possible of testing and verification code, in order to save time and effort in implementation.
Also, as many tasks as possible should be automated by scripts, to save time in manual labor for the engineers working on the development.
All that enables an efficient development cycle of the product.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NOTES:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FEEDBACK, Meeting 07-16-2021
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%formatting:
%- absätze überall gleich (mit oder ohne leerzeile)
%references:
%- hauptsache überall gleich (Fig.2.3 oder Sec.7.1 oder Eq.3 oder Chpt.4)
%- literature refs at the beginning of a chapter/section
%  like "this chapter is based on [1][4][5]."
%  or at the end of the last sentence like "...the end of this sentence. [7]"
%
%Allgemeiner Teil / Theorie:
% zusätzliches kapitel:
%   system design ansätze
%   - from algo to VHDL (book: vom algorithmus zur hardware)
%   - matlab to VHDL
%   - systementwuf richtung test driven design
%   --> design space exploration
%
%
% ganze Arbeit aufhängen an:
%   main objective: fit all the aspects (algorithm, impl, testing) into
%                   a single project
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO General
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% ## unify all graphs and diagrams
%       - all gray; use exact same gray tone; eliminate the yellow?
%
% ## check all abbreviation and where they are introduced the first time
%       - introduce only once, like "device under test (DUT)",
%         then use the abbreviation only
%

### 2021-07-22 doc/thesis/chapters/system-design-process.tex
update
move the entire section vhdl:testbench:general to hls:testbench:general
axi lite register engine

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The SIMILAR Process}
%TODO: maybe include additional facts from https://slideplayer.com/slide/14327503/

@@

This step combines multiple single components into a larger, integrated system, which can then be treated as a whole.
In order to be able to do that, interfaces between the components and subsystems need to be defined.
Optimally, these interfaces are designed in a way that the amount of data that needs to be exchanged is kept to a minimum.
It is of advantage, if a subsystem only transfers finished products that it produced to another subsystem.
The aim to develop simple interfaces is of special advantage in systems that include a feedback loop.
There, managing the feedback loop connections is easier if there is a clear interface, so the loop can be connected around an entire subsystem, instead of interconnecting within the subsystems.

@@

In this thesis, only the HLS of plain \cplusplus\ is covered.
SystemC is not discussed, since it may potentially be less important in the future.
In the latest Xilinx HLS tools 'Vitis HLS' and 'Vivado HLS', the language SystemC is already deprecated \cite{VivadoHlsSystemC}.\\

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The SIMILAR Process}
\label{sec:SimilarProcess}
%TODO: maybe include additional facts from https://slideplayer.com/slide/14327503/

@@

This step combines multiple single components into a larger, integrated system, which can then be treated as a whole.
In order to be able to do that, interfaces between the components and subsystems need to be defined.
Ideally, these interfaces are designed in a way that the amount of data that needs to be exchanged is kept to a minimum.
It is of advantage, if a subsystem only transfers finished products that it produced to another subsystem.
The aim to develop simple interfaces is of special advantage in systems that include a feedback loop.
There, managing the feedback loop connections is easier if there is a clear interface, so the loop can be connected around an entire subsystem, instead of interconnecting within the subsystems.

@@

In this thesis, only the HLS of plain \cplusplus\ is covered.
SystemC is not discussed, since it may potentially be less important in the future.
In the latest Xilinx HLS tools 'Vitis HLS' and 'Vivado HLS', the language SystemC is already deprecated \cite{VivadoHlsDeprecatesSystemC}.\\
